TEMPERATURES AND METALLICITIES FOR 10,000+ M DWARFS IN THE \apogee\ SURVEY

### 2018-08-13 paper/draft.tex
add table units

\begin{longrotatetable}
\begin{deluxetable*}{cccccccccc}
\tabletypesize{\scriptsize}
\tablecaption{Temperatures/Metallicities (from Mann-trained model), and spectral types (from West-trained model) for the sample 10,311 APOGEE M dwarfs, as well as goodness of fit for the respective models. \label{test_results_table}}
\tablehead{\colhead{APOGEE ID} & \colhead{Gaia\ ID} & \colhead{RA}  & \colhead{DEC} & \colhead{\teff} 
& \colhead{[Fe/H]}  & \colhead{SPT} & \colhead{$\chi^2$ Mann} & \colhead{$\chi^2$ West} & \colhead{\nodata}}   
\startdata
2M00432365+0332534 & 413814124681430528  & 10.848967  & 3.548273   & 3417 & 0.18  & 3.0 & 7910  & 7912   & \nodata \\
2M10382316+2457051 & 808931427773946112  & 159.596215 & 24.951373  & 3358 & -0.25 & 3.4 & 19051 & 25518  & \nodata \\
2M09364698+5602332 & 598955557617293440  & 144.195513 & 56.042461  & 3819 & 0.01  & 1.5 & 7981  & 6894   & \nodata \\
2M12165176+1543232 & 1538883006881701120 & 184.215466 & 15.723067  & 3948 & 0.16  & 0.7 & 25354 & 19983  & \nodata \\
2M18501195+4809327 & 2037435595069990016 & 282.549868 & 48.15976   & 3899 & 0.24  & 0.9 & 7205  & 7151   & \nodata \\
2M07572656+4703318 & 682241540493118080  & 119.360502 & 47.05852   & 3636 & -0.17 & 2.4 & 38430 & 45625  & \nodata \\
2M11083992+1112503 & 1536026200794333696 & 167.166344 & 11.213979  & 3949 & 0.1   & 0.8 & 21165 & 17506  & \nodata \\
2M12135300+1419452 & 3695183295027782656 & 183.470871 & 14.32924   & 3824 & 0.13  & 1.3 & 35018 & 21010  & \nodata \\
2M12273816-0049437 & 3682549562826659456 & 186.909269 & -0.828949  & 3715 & 0.04  & 1.8 & 14179 & 10656  & \nodata \\
2M10513639-0150064 & 777824835073481984  & 162.901465 & -1.835273  & 3997 & -0.15 & 1.2 & 80915 & 75157  & \nodata \\
2M02442390-1352593 & 447040266556331008  & 41.099824  & -13.883403 & 3676 & -0.28 & 2.3 & 41375 & 56704  & \nodata \\
2M06281785+0940439 & 65792100044278400   & 97.074558  & 9.678234   & 3659 & -0.29 & 2.3 & 78827 & 118883 & \nodata \\
2M13441275+5538012 & 1551387099791031552 & 206.053693 & 55.633288  & 3856 & -0.1  & 1.6 & 50070 & 45895  & \nodata \\
2M12473762+1107449 & 1251277737449848064 & 191.906593 & 11.129187  & 3244 & -0.42 & 4.0 & 30184 & 47020  & \nodata \\
2M01274162+8435576 & 523638809262601216  & 21.924655  & 84.599233  & 3534 & 0.07  & 2.6 & 15529 & 15113  & \nodata \\
2M13464494+4034158 & 1247733770955275008 & 206.686943 & 40.571056  & 3731 & -0.16 & 2.1 & 53196 & 50765  & \nodata \\
2M00504161+0219408 & 2376325179183866240 & 12.673481  & 2.327846   & 3745 & 0.4   & 1.4 & 76966 & 52035  & \nodata \\
2M14494090+3201268 & 1292097793826595328 & 222.420454 & 32.023994  & 3228 & 0.0   & 3.9 & 28733 & 38112  & \nodata \\
2M16434969-0123117 & 1406510018874952960 & 250.957083 & -1.386602  & 3669 & 0.03  & 2.0 & 22346 & 17186  & \nodata \\
2M13444356+1655384 & 1565587017583214464 & 206.18144  & 16.927287  & 3652 & 0.13  & 2.1 & 47828 & 40933  & \nodata \\
2M08162613+3250515 & 3053990410555781120 & 124.108745 & 32.84736   & 3837 & -0.15 & 1.8 & 30389 & 35103  & \nodata \\
2M10414608+2435412 & 3758656623830055168 & 160.441928 & 24.594731  & 4020 & -0.19 & 1.1 & 41857 & 36934  & \nodata \\
2M14373854+5014502 & 1188221157913600384 & 219.410555 & 50.247523  & 3380 & -0.13 & 3.2 & 35397 & 41989  & \nodata \\
2M13444572+0012349 & 1475140469529542656 & 206.19035  & 0.209419   & 3782 & -0.28 & 2.0 & 12155 & 12707  & \nodata \\
2M21275902+1332166 & 1817731181599810944 & 321.995889 & 13.537918  & 3997 & 0.18  & 0.6 & 78906 & 67503 & \nodata \\
\nodata & \nodata & \nodata & \nodata & \nodata & \nodata & \nodata & \nodata & \nodata & \nodata
\enddata
\end{deluxetable*}
\end{longrotatetable}

@@

\tablehead{\colhead{\nodata} & \colhead{$\varpi$} & \colhead{$\sigma_\varpi$} & \colhead{$\mu_\alpha$}  & \colhead{$\sigma_{\mu\alpha}$} & \colhead{$\mu_\delta$} & \colhead{$\sigma_{\mu\delta}$}  & \colhead{$v_{los}$} & \colhead{\nodata}}   

@@

\nodata & 1.0588602017295168  & 0.03531208113851025  & -33.94690128799879  & 0.14827664116823172 & -67.52530689866221  & 0.10435398589835812  & 46.9949     & \nodata \\
\nodata & 0.18385583304779304 & 0.027656036948018537 & -11.332297533362624 & 0.04670812215256213 & -12.924309762298892 & 0.0502953286981639   & -13.1057   & \nodata \\

@@

\begin{longrotatetable}
\begin{deluxetable*}{cccccccccc}
\tabletypesize{\scriptsize}
\tablecaption{\apogee\ $JHK$ and \gaia\ $G$, $BP$, $RP$ photometric measurements.}
\tablehead{\colhead{\nodata} & \colhead{$J$} & \colhead{$H$} & \colhead{$K$} & \colhead{$G$} & \colhead{$BP$} & \colhead{$RP$}}   
\startdata
\nodata & 12.83199977874756  & 12.175999641418455 & 11.96500015258789  & 13.415744          & 14.226433           & 12.53435            \\
\nodata & 14.255999565124512 & 13.72599983215332  & 13.40999984741211  & 12.228349          & 12.702468           & 11.614723           \\
\nodata & 11.791999816894533 & 11.104999542236328 & 10.967000007629396 & 10.691218          & 11.139357           & 10.104778           \\
\nodata & 13.706000328063965 & 13.013999938964846 & 12.895999908447266 & 12.420532          & 12.90665            & 11.800449           \\
\nodata & 11.616999626159668 & 10.946000099182127 & 10.751999855041504 & 12.908026          & 13.56541            & 12.142124           \\
\nodata & 11.312999725341795 & 10.663999557495117 & 10.508000373840332 & 10.826382          & 10.85745            & 10.774274           \\
\nodata & 13.128999710083008 & 12.498000144958494 & 12.32699966430664  & 14.534789          & 15.185692           & 13.744579           \\
\nodata & 13.538000106811525 & 12.902999877929688 & 12.762999534606935 & 14.004284          & 14.160915           & 13.288598           \\
\nodata & 12.69499969482422  & 12.036999702453613 & 11.86299991607666  & 14.93699           & 15.395644           & 14.318204           \\
\nodata & 12.53499984741211  & 11.843999862670898 & 11.732000350952148 & 10.015749          & 10.34129            & 9.559692            \\
\nodata & 12.536999702453613 & 11.928000450134276 & 11.682000160217285 & 13.735478          & 14.700515           & 12.765027           \\
\nodata & 11.274999618530273 & 10.717000007629396 & 10.515000343322754 & 11.817871          & 12.467115           & 11.063624           \\
\nodata & 10.21399974822998  & 9.600000381469727  & 9.407999992370604  & 13.178638          & 13.876391           & 12.384415           \\
\nodata & 14.201000213623047 & 13.718000411987305 & 13.46500015258789  & 12.388862          & 12.901998           & 11.731835           \\
\nodata & 13.104000091552734 & 12.43000030517578  & 12.256999969482422 & 8.78063            & 8.920993            & 8.569135            \\
\nodata & 11.628999710083008 & 10.996000289916992 & 10.802000045776367 & 15.246564          & 16.136223           & 14.321473           \\
\nodata & 12.312999725341795 & 11.618000030517578 & 11.38599967956543  & 11.829312          & 12.26109            & 11.258054           \\
\nodata & 12.07800006866455  & 11.48799991607666  & 11.237000465393066 & 13.222831          & 13.763299           & 12.547942           \\
\nodata & 13.682000160217285 & 12.944000244140625 & 12.72700023651123  & 12.266772          & 12.872325           & 11.548589           \\
\nodata & 13.501999855041506 & 12.85099983215332  & 12.64900016784668  & 10.416036          & 10.922305           & 9.781987            \\
\nodata & 13.95300006866455  & 13.29300022125244  & 13.10099983215332  & 13.099073          & 13.74368            & 12.342266           \\
\nodata & 14.246000289916992 & 13.595000267028807 & 13.397000312805176 & 11.854821          & 12.39487            & 11.183031           \\
\nodata & 13.241999626159668 & 12.670999526977539 & 12.432000160217285 & 13.945971          & 14.459273           & 13.295053           \\
\nodata & 14.10200023651123  & 13.41800022125244  & 13.29800033569336  & 11.466022          & 12.018276           & 10.803698           \\
\nodata & 12.576000213623047 & 11.892000198364258 & 11.701000213623047 & 14.51524           & 15.042348           & 13.839335    \\
\nodata & \nodata & \nodata & \nodata & \nodata & \nodata & \nodata
\enddata
\end{deluxetable*}
\end{longrotatetable}

>>>>

\begin{longrotatetable}
\begin{deluxetable*}{cccccccccc}
\tabletypesize{\scriptsize}
\tablecaption{Temperatures/Metallicities (from Mann-trained model), and spectral types (from West-trained model) for the sample 10,311 APOGEE M dwarfs, as well as goodness of fit for the respective models. \label{test_results_table}}
\tablehead{\colhead{APOGEE ID} & \colhead{Gaia\ ID} & \colhead{RA}  & \colhead{DEC} & \colhead{\teff} & \colhead{[Fe/H]}  & \colhead{SPT} & \colhead{$\chi^2$ Mann} & \colhead{$\chi^2$ West} & \colhead{\nodata} \\
 &  & (deg)  & (deg) & (K) & (dex) &  &  &  & }   
\startdata
2M00432365+0332534 & 413814124681430528  & 10.848967  & 3.548273   & 3417 & 0.18  & 3.0 & 7910  & 7912   & \nodata \\
2M10382316+2457051 & 808931427773946112  & 159.596215 & 24.951373  & 3358 & -0.25 & 3.4 & 19051 & 25518  & \nodata \\
2M09364698+5602332 & 598955557617293440  & 144.195513 & 56.042461  & 3819 & 0.01  & 1.5 & 7981  & 6894   & \nodata \\
2M12165176+1543232 & 1538883006881701120 & 184.215466 & 15.723067  & 3948 & 0.16  & 0.7 & 25354 & 19983  & \nodata \\
2M18501195+4809327 & 2037435595069990016 & 282.549868 & 48.15976   & 3899 & 0.24  & 0.9 & 7205  & 7151   & \nodata \\
2M07572656+4703318 & 682241540493118080  & 119.360502 & 47.05852   & 3636 & -0.17 & 2.4 & 38430 & 45625  & \nodata \\
2M11083992+1112503 & 1536026200794333696 & 167.166344 & 11.213979  & 3949 & 0.1   & 0.8 & 21165 & 17506  & \nodata \\
2M12135300+1419452 & 3695183295027782656 & 183.470871 & 14.32924   & 3824 & 0.13  & 1.3 & 35018 & 21010  & \nodata \\
2M12273816-0049437 & 3682549562826659456 & 186.909269 & -0.828949  & 3715 & 0.04  & 1.8 & 14179 & 10656  & \nodata \\
2M10513639-0150064 & 777824835073481984  & 162.901465 & -1.835273  & 3997 & -0.15 & 1.2 & 80915 & 75157  & \nodata \\
2M02442390-1352593 & 447040266556331008  & 41.099824  & -13.883403 & 3676 & -0.28 & 2.3 & 41375 & 56704  & \nodata \\
2M06281785+0940439 & 65792100044278400   & 97.074558  & 9.678234   & 3659 & -0.29 & 2.3 & 78827 & 118883 & \nodata \\
2M13441275+5538012 & 1551387099791031552 & 206.053693 & 55.633288  & 3856 & -0.1  & 1.6 & 50070 & 45895  & \nodata \\
2M12473762+1107449 & 1251277737449848064 & 191.906593 & 11.129187  & 3244 & -0.42 & 4.0 & 30184 & 47020  & \nodata \\
2M01274162+8435576 & 523638809262601216  & 21.924655  & 84.599233  & 3534 & 0.07  & 2.6 & 15529 & 15113  & \nodata \\
2M13464494+4034158 & 1247733770955275008 & 206.686943 & 40.571056  & 3731 & -0.16 & 2.1 & 53196 & 50765  & \nodata \\
2M00504161+0219408 & 2376325179183866240 & 12.673481  & 2.327846   & 3745 & 0.4   & 1.4 & 76966 & 52035  & \nodata \\
2M14494090+3201268 & 1292097793826595328 & 222.420454 & 32.023994  & 3228 & 0.0   & 3.9 & 28733 & 38112  & \nodata \\
2M16434969-0123117 & 1406510018874952960 & 250.957083 & -1.386602  & 3669 & 0.03  & 2.0 & 22346 & 17186  & \nodata \\
2M13444356+1655384 & 1565587017583214464 & 206.18144  & 16.927287  & 3652 & 0.13  & 2.1 & 47828 & 40933  & \nodata \\
2M08162613+3250515 & 3053990410555781120 & 124.108745 & 32.84736   & 3837 & -0.15 & 1.8 & 30389 & 35103  & \nodata \\
2M10414608+2435412 & 3758656623830055168 & 160.441928 & 24.594731  & 4020 & -0.19 & 1.1 & 41857 & 36934  & \nodata \\
2M14373854+5014502 & 1188221157913600384 & 219.410555 & 50.247523  & 3380 & -0.13 & 3.2 & 35397 & 41989  & \nodata \\
\nodata & \nodata & \nodata & \nodata & \nodata & \nodata & \nodata & \nodata & \nodata & \nodata
\enddata
\end{deluxetable*}
\end{longrotatetable}

@@

\tablehead{\colhead{\nodata} & \colhead{$\varpi$} & \colhead{$\sigma_\varpi$} & \colhead{$\mu_\alpha$}  & \colhead{$\sigma_{\mu\alpha}$} & \colhead{$\mu_\delta$} & \colhead{$\sigma_{\mu\delta}$}  & \colhead{$v_{los}$} & \colhead{\nodata} \\
 & (mas) & (mas) & (mas/yr)  & (mas/yr) & (mas/yr) & (mas/yr)  & (km/s) & \colhead{\nodata}}   

@@

@@

\begin{longrotatetable}
\begin{deluxetable*}{cccccccccc}
\tabletypesize{\scriptsize}
\tablecaption{\apogee\ $JHK$ and \gaia\ $G$, $BP$, $RP$ photometric measurements.}
\tablehead{\colhead{\nodata} & \colhead{$J$} & \colhead{$H$} & \colhead{$K$} & \colhead{$G$} & \colhead{$BP$} & \colhead{$RP$}}   
\startdata
\nodata & 12.83199977874756  & 12.175999641418455 & 11.96500015258789  & 13.415744          & 14.226433           & 12.53435            \\
\nodata & 14.255999565124512 & 13.72599983215332  & 13.40999984741211  & 12.228349          & 12.702468           & 11.614723           \\
\nodata & 11.791999816894533 & 11.104999542236328 & 10.967000007629396 & 10.691218          & 11.139357           & 10.104778           \\
\nodata & 13.706000328063965 & 13.013999938964846 & 12.895999908447266 & 12.420532          & 12.90665            & 11.800449           \\
\nodata & 11.616999626159668 & 10.946000099182127 & 10.751999855041504 & 12.908026          & 13.56541            & 12.142124           \\
\nodata & 11.312999725341795 & 10.663999557495117 & 10.508000373840332 & 10.826382          & 10.85745            & 10.774274           \\
\nodata & 13.128999710083008 & 12.498000144958494 & 12.32699966430664  & 14.534789          & 15.185692           & 13.744579           \\
\nodata & 13.538000106811525 & 12.902999877929688 & 12.762999534606935 & 14.004284          & 14.160915           & 13.288598           \\
\nodata & 12.69499969482422  & 12.036999702453613 & 11.86299991607666  & 14.93699           & 15.395644           & 14.318204           \\
\nodata & 12.53499984741211  & 11.843999862670898 & 11.732000350952148 & 10.015749          & 10.34129            & 9.559692            \\
\nodata & 12.536999702453613 & 11.928000450134276 & 11.682000160217285 & 13.735478          & 14.700515           & 12.765027           \\
\nodata & 11.274999618530273 & 10.717000007629396 & 10.515000343322754 & 11.817871          & 12.467115           & 11.063624           \\
\nodata & 10.21399974822998  & 9.600000381469727  & 9.407999992370604  & 13.178638          & 13.876391           & 12.384415           \\
\nodata & 14.201000213623047 & 13.718000411987305 & 13.46500015258789  & 12.388862          & 12.901998           & 11.731835           \\
\nodata & 13.104000091552734 & 12.43000030517578  & 12.256999969482422 & 8.78063            & 8.920993            & 8.569135            \\
\nodata & 11.628999710083008 & 10.996000289916992 & 10.802000045776367 & 15.246564          & 16.136223           & 14.321473           \\
\nodata & 12.312999725341795 & 11.618000030517578 & 11.38599967956543  & 11.829312          & 12.26109            & 11.258054           \\
\nodata & 12.07800006866455  & 11.48799991607666  & 11.237000465393066 & 13.222831          & 13.763299           & 12.547942           \\
\nodata & 13.682000160217285 & 12.944000244140625 & 12.72700023651123  & 12.266772          & 12.872325           & 11.548589           \\
\nodata & 13.501999855041506 & 12.85099983215332  & 12.64900016784668  & 10.416036          & 10.922305           & 9.781987            \\
\nodata & 13.95300006866455  & 13.29300022125244  & 13.10099983215332  & 13.099073          & 13.74368            & 12.342266           \\
\nodata & 14.246000289916992 & 13.595000267028807 & 13.397000312805176 & 11.854821          & 12.39487            & 11.183031           \\
\nodata & 13.241999626159668 & 12.670999526977539 & 12.432000160217285 & 13.945971          & 14.459273           & 13.295053           \\
\nodata & \nodata & \nodata & \nodata & \nodata & \nodata & \nodata
\enddata
\end{deluxetable*}
\end{longrotatetable}
